Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-02-24 ms/Accessory/Wenk-Accessory-SI.Rnw
remove SeaveOpts line (self-inserts whenever I push button "compile PDF in RStudio)
started adding in pdfs of plant maps. All the others are in the same folder, but didn't add them in until I'm sure syntax is correct.

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot_graph(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(BOLE_GraphMaps$graph)
@
\caption{Map of parts for \emph{Boronia ledifolia}}
\label{fig:map Boronia ledifolia}
\end{figure}

>>>>

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(BAER_GraphMaps$graph)
  ###\includegraphics{"../../ms/Accessory/output/BAER.pdf"}
@
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

@@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
  plot_graph(BOLE_GraphMaps$graph)
  ###\includegraphics{"../../ms/Accessory/output/BOLE.pdf"}
@
\caption{Map of parts for \emph{Boronia ledifolia}}
\label{fig:map Boronia ledifolia}
\end{figure}
